An Open Repository of Real-Time COVID-19 Indicators

### 2021-06-13 indicators/paper/paper.tex
Update discussion of signals

We receive data daily from healthcare partners, technology companies, and from
surveys conducted daily by Delphi in partnership with Facebook. These data
sources provide information not available from standard public health reporting
or other common sources, such as:
\begin{description}
\item[Health Insurance Claims] Based on de-identified medical insurance claims
  from Change Healthcare and other health system partners, we release indicators
  on the estimated percentage of covered outpatient visits and hospitalizations
  that involved COVID diagnoses or symptoms.
\item[Internet-Based Surveys] Conducted in partnership with Facebook, Delphi's
  COVID Tracking and Impact Survey receives about 50,000 responses daily, and
  has received over 20 million responses since April 2020 \cite{DelphiSurvey,
    Kreuter:2020}. From the surveys, we construct indicators on symptoms,
  social distancing, vaccination, and other attitudes and behaviors related to
  COVID.
\item[COVID Antigen Tests] Based on data from Quidel, a major manufacturer of
  COVID antigen tests in the United States, we calculate and release
  (Quidel-specific) test volumes and positivity rates.
\item[Search Trends] Based on Google's COVID-19 Search Trends symptoms data set
  \cite{GoogleSymptoms}, we provide indicators reflecting COVID-related search
  activity.
\item[Mobility Data] Cell phone mobility data is collected by SafeGraph
  \cite{SafeGraphSD, SafeGraphPatterns}, and is available to researchers under a
  data use agreement; we aggregate it to the county level and make indicators
  publicly available.
\end{description}

We also scrape data accessible from other public sources, such as cases and
deaths data aggregated from public reporting by JHU CSSE \cite{Dong:2020} and by
USAFacts \cite{USAFacts}, so that we can track revisions and updates to this data
(see Section~\ref{subsec:revision_tracking}).

Together, we collect TODO signals from TODO distinct sources, aggregate them,
and provide them in a single common format for public access. This hence
provides a common format both for unique data streams not available elsewhere
and for public data streams, enabling efficient comparison and modeling use.

A summary of the data sources we currently receive and make available is
presented in Table~\ref{data-sources}, and detailed documentation of the signals
available from each source is available at
\url{https://cmu-delphi.github.io/delphi-epidata/api/covidcast_signals.html}.

\begin{table*}
\centering
\caption{Data sources available in Delphi's COVIDcast API \cite{CovidcastAPI},
  as of date of publication. The first group of data sources are produced by
  Delphi from data not otherwise available publicly (or only available in
  limited form); the second group is mirrored from public sources.}
\begin{tabular}{>{\raggedright}p{1.2in} p{4.0in} r >{\raggedright\arraybackslash}p{0.5in}}\toprule
\textbf{Data source} & \textbf{Signals available} & \textbf{First date} &
\textbf{Resolution} \\\midrule
  % Exclusive data
  Change Healthcare & Percentage of outpatient visits with COVID diagnostic codes
or codes indicating COVID-like symptoms. Based on de-identified claims data
processed by Change Healthcare. & 2020-02-01 & County$^*$ \\
  Doctor Visits & Percentage of outpatient visits primarily about COVID-like
symptoms, based on de-identified claims data provided by health system
partners. & 2020-02-01 & County$^*$ \\
  Hospital Admissions & Percentage of new hospital admissions with COVID
diagnostic codes, based on de-identified claims data provided by health system
partners. & 2020-02-01 & County$^{**}$\\
  Quidel & Test positivity rates for COVID-19 antigen tests produced by
Quidel. & 2020-05-26 & County$^{**}$ \\
  SafeGraph & Mobility metrics, such as time away from home or visits to bars
and restaurants, based on cell phone mobility data collected by SafeGraph
\cite{SafeGraphSD, SafeGraphPatterns}. & 2019-01-01 & County \\
 COVID Tracking and Impact Survey & COVID symptoms, social distancing behaviors,
mental health, economic impact, behavior (e.g., mask-wearing, vaccination
attitudes), and COVID testing signals based on daily surveys conducted
nationally by Delphi through Facebook \cite{DelphiSurvey, Kreuter:2020}. &
2020-04-06 & County$^{**}$ \\
  \midrule
    % Mirrored data from other sources
  Health \& Human Services & Counts of hospital admissions due to confirmed or
suspected COVID-19, as reported by the Department of Health \& Human Services. &
2019-12-31 & State \\
    COVID Act Now & COVID-19 testing results, such as positivity and number of
tests, compiled by COVID Act Now from CDC reporting. & 2020-03-02 &
County$^*$ \\
  Google Symptoms & Trends in Google search volume for terms related to anosmia
and ageusia (loss of smell or taste), which correlate with COVID activity, based
on data shared by Google \cite{GoogleSymptoms}. & 2020-02-13 & County$^{***}$ \\
  Cases and Deaths & Confirmed COVID-19 cases and deaths, compiled by JHU CSSE
\cite{Dong:2020} and by USAFacts \cite{USAFacts}. & 2020-01-22 & County \\
  NCHS Mortality & Weekly totals of deaths broken down by cause, such as COVID,
flu, or pneumonia, compiled by the National Center for Health Statistics [TODO
cite]. & 2020-01-26 & State \\
    \bottomrule
\end{tabular}
% TODO PNAS wants a short title above and caption below, but they can't possibly
% mean for the caption to be formatted so weirdly...
\addtabletext{Location availability often drops lower for some times and
  signals, e.g., due to variable reporting volume. $^*$Available at $>60$\% of
  counties; $^{**}$available at 20--60\% of counties; $^{***}$available at
  $<20$\% of counties.}
\label{data-sources}
\end{table*}

>>>>

We receive data daily from healthcare partners, technology companies, and from
surveys conducted daily by Delphi in partnership with Facebook. These data
sources provide information not available from standard public health reporting
or other common sources, such as:

\paragraph{Health Insurance Claims} Based on de-identified medical insurance 
claims from Change Healthcare and other health system partners, we release
indicators on the estimated percentage of covered outpatient visits and
hospitalizations that involved COVID diagnoses or symptoms.

\paragraph{Internet-Based Surveys} Conducted in partnership with Facebook,
Delphi's COVID Tracking and Impact Survey receives about 50,000 responses daily,  
and has received over 20 million responses since April 2020 \cite{DelphiSurvey,
  Kreuter:2020}. From the surveys, we construct indicators on symptoms, social 
distancing, vaccination, and other attitudes and behaviors related to COVID.

\paragraph{COVID Antigen Tests} Based on data from Quidel, a manufacturer of
COVID antigen tests in the United States, we calculate and release
(Quidel-specific) test volumes and positivity rates.

\paragraph{Search Trends} Based on Google's COVID-19 Search Trends data set
\cite{GoogleSymptoms}, we provide indicators reflecting COVID-related search  
activity.

\paragraph{Mobility Data} SafeGraph, a company that collects geospatial data
from smartphone apps, calculates COVID-related mobility signals
\cite{SafeGraphSD, SafeGraphPatterns} and makes it available to researchers
under a data use agreement; we aggregate (some of) these signals to the county
level and make them publicly available.

\medskip
We also scrape data accessible from other public sources, such as cases and
deaths data aggregated from public reporting by JHU CSSE \cite{Dong:2020} and by
USAFacts \cite{USAFacts}, so that we can track revisions and updates to this data
(see Section~\ref{subsec:revision_tracking}).

Altogether, we collect 110 signals from 12 distinct sources, aggregate and
process them, and provide them in a common format for public access. This
unifies both unique (not available anywhere else) and standard COVID data
streams into a single common format, enabling efficient comparison and modeling.
A summary of the data sources and signals in the API is in
Table~\ref{data-sources}, and detailed documentation is available at
\url{https://cmu-delphi.github.io/delphi-epidata/api/covidcast_signals.html}.

\begin{table*}
\centering
\caption{Data sources available in Delphi's COVIDcast API \cite{CovidcastAPI},
  as of date of publication. The first group of data sources are produced by
  Delphi from data not otherwise available publicly (or only available in
  limited form); the second group is mirrored from public sources.}
\begin{tabular}{>{\raggedright}p{1.2in} p{4.0in} l >{\raggedright\arraybackslash}p{0.5in}}
\toprule
\textbf{Data source} & \textbf{Signals available} & \textbf{First date} &
\textbf{Resolution} \\\midrule
  % Exclusive data
  Change Healthcare & Percentage of outpatient visits with COVID diagnostic codes
or codes indicating COVID-like symptoms. Based on de-identified claims data
processed by Change Healthcare. & 2020-02-01 & County$^*$ \\
  Doctor Visits & Percentage of outpatient visits primarily about COVID-like
symptoms, based on de-identified claims data provided by health system
partners. & 2020-02-01 & County$^*$ \\
  Hospital Admissions & Percentage of new hospital admissions with COVID
diagnostic codes, based on de-identified claims data provided by health system
partners. & 2020-02-01 & County$^{**}$\\
  Quidel & Test positivity rates for COVID-19 antigen tests produced by
Quidel. & 2020-05-26 & County$^{**}$ \\
  SafeGraph & Mobility metrics, such as time away from home or visits to bars
and restaurants, based on cell phone mobility data collected by SafeGraph
\cite{SafeGraphSD, SafeGraphPatterns}. & 2019-01-01 & County \\
 COVID Tracking and Impact Survey & COVID symptoms, social distancing behaviors,
mental health, economic impact, behavior (e.g., mask-wearing, vaccination
attitudes), and COVID testing signals based on daily surveys conducted
nationally by Delphi through Facebook \cite{DelphiSurvey, Kreuter:2020}. &
2020-04-06 & County$^{**}$ \\
  \midrule
    % Mirrored data from other sources
  Health \& Human Services & Counts of hospital admissions due to confirmed or
suspected COVID-19, as reported by the Department of Health \& Human Services. &
2019-12-31 & State \\
COVID Act Now & COVID-19 testing results, such as positivity rate and number of
 tests, compiled by COVID Act Now from CDC reporting. & 2020-03-02 & 
County$^*$ \\
  Google Symptoms & Trends in Google search volume for terms related to anosmia
and ageusia (loss of smell or taste), which correlate with COVID activity, based
on data shared by Google \cite{GoogleSymptoms}. & 2020-02-13 & County$^{***}$ \\
  Cases and Deaths & Confirmed COVID-19 cases and deaths, compiled by JHU CSSE
\cite{Dong:2020} and by USAFacts \cite{USAFacts}. & 2020-01-22 & County \\
  NCHS Mortality & Weekly totals of deaths broken down by cause, such as COVID,
flu, or pneumonia, compiled by the National Center for Health Statistics [TODO
cite]. & 2020-01-26 & State \\
    \bottomrule
\end{tabular}
\addtabletext{$^*$Available at $>60$\% of counties; $^{**}$available at 20--60\%
  of counties; $^{***}$available at $<20$\% of counties.  For some signals,
  location availability varies over time, e.g., due to variable reporting
  volume.}
\label{data-sources}
\end{table*}
